Early range shifts in transboundary fish stocks challenge their management under climate change

### 2021-03-10 Scripts/Manuscript.Rmd
changes to title page

---
title: Identifying Shifts in the Share Distribution of Transboundary Fish Stocks to Lead Time for Policy Response Under Climate Change
subtitle: Challenges to transboundary fisheries under climate change
author: 'Authors: Juliano Palacios-Abrantes*^1^, Thomas Frölicher^2,3^, Gabriel Reygondeau^1^, U. Rashid Sumaila^1^, Alessandro Tagliabue^4^, Colette Wabnitz^1,5^, and William W.L. Cheung^1^'
date: 'Affiliations: ^1^Institute for the Oceans and Fisheries, University of British Columbia, Vancouver, Canada. ^2^Climate and Environmental Physics, Physics Institute, University of Bern. ^3^Oeschger Centre for Climate Change Research, University of Bern, Switzerland. ^4^School of Environmental Sciences, University of Liverpool. ^5^Center for Ocean Solutions, Stanford University, Stanford, United States'
output:
  # word_document:
    # reference_docx: ../References/template.docx
  pdf_document: default
bibliography: ../References/ToE_Ref.bib
csl: ../References/science.csl
header-includes:
- \usepackage{amsmath}
- \usepackage{float} # Use the 'float' package
- \floatplacement{figure}{H} # Make every figure with caption = h
---

>>>>

---
title: Early range shifts in transboundary fish stocks challenge their management under climate change
# subtitle: Changes in sharing of transboundary fisheries under climate change
author: 'Authors: Juliano Palacios-Abrantes^1*^, Thomas Frölicher^2,3^, Gabriel Reygondeau^1^, U. Rashid Sumaila^1^, Alessandro Tagliabue^4^, Colette Wabnitz^1,5^, and William W.L. Cheung^1^'
date: 'Affiliations: ^1^Institute for the Oceans and Fisheries, University of British Columbia, Vancouver, Canada. ^2^Climate and Environmental Physics, Physics Institute, University of Bern. ^3^Oeschger Centre for Climate Change Research, University of Bern, Switzerland. ^4^School of Environmental Sciences, University of Liverpool. ^5^Stanford Center for Ocean Solutions, Stanford University, Stanford, United States'
output:
  # bookdown::word_document2
    reference_docx: ../References/template.docx
  # pdf_document: default
bibliography: ../References/ToE_Ref.bib
csl: ../References/science.csl
header-includes:
- \usepackage{amsmath}
- \usepackage{float} # Use the 'float' package
- \floatplacement{figure}{H} # Make every figure with caption = h
---
